---
title: "PSY 8712 Week 8 Project"
author: "Delaney Ross"
output:
  html_document:
    output_dir: out
---

# **Reproducible Image and Online Resources:**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link.](https://mybinder.org/v2/gh/ross0778/psy8712-week8/HEAD)
An interactive web app is available by [clicking this link instead.](https://8d76t4-delaney-ross.shinyapps.io/shiny_week8/)

# **Script Settings and Resources**
```{r script_settings, echo = TRUE, message = FALSE, warning = FALSE, results = 'hide'}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# **Data Import and Cleaning**
This section imports and cleans the data file, converts times to POSIX format, converts condition and gender to factor, reverse codes q5, and finds row means for following calculations. I used mutate to make these conversions as it seemed the most efficient method and I subtracted q5 from the sum of the maximum and minimum of this question as it was the most straightforward way to reverse code the column.
```{r data_import, echo = TRUE}
week8_tbl <- read.csv("../data/week3.csv") %>% 
  mutate(
    timeStart = ymd_hms(timeStart),
    timeEnd = ymd_hms(timeEnd),
    condition = factor(condition,
                       levels = c("A", "B", "C"),
                       labels = c("Block A", "Block B", "Block C")),
    gender = factor(gender,
                    levels = c("M", "F"),
                    labels = c("Male", "Female")),
    q5 = (1 + 5) - q5,
    mq1q6 = rowMeans(pick(q1:q6)),
    mq8q10 = rowMeans(pick(q8:q10))
  )
```

# **Visualization**
This section displays the data from q1 through q6 as well as a scatterplot of the mean scores of q1 through q6 and the mean scores of q8 through q10. I used select to display the data contained within q1-q6, geom_point to create the scatterplot, and geom_smooth() in order to create the regression line.
```{r visualization, echo = FALSE, message = FALSE}
week8_tbl %>% select(q1:q6)
week8_tbl %>% 
  ggplot(aes(x = mq1q6, y = mq8q10)) +
  geom_point() +
  geom_smooth(method = "lm", color = "purple")
```

# **Analysis**
This section runs the correlation between the mean scores of q1 through q6 and the mean scores of q8 through q10. I used the sub() function in order to pattern match, used regex to identify the pattern, used "" to remove anything that matches "^0", and I used formatC in order to format the correlation.
```{r analysis, echo = FALSE}
mcor <- cor.test(week8_tbl$mq1q6, week8_tbl$mq8q10)
mcor2 <- sub("^0", "", formatC(round(mcor$estimate, 2), format = "f", digits = 2))
p_cor <- mcor$p.value
```
I observed a correlation of `r mcor2` between the mean scores of Q1-Q6 and the mean scores of Q8-Q10.The p-value was `r round(p_cor, 2)`, which `r ifelse(p_cor < .05, "is", "is not")` statistically significant at $\alpha = .05$, indicating that the relationship between the two scales `r ifelse(p_cor < .05, "is", "is not")` due to chance.

# **Data Export**
```{r data_export, echo = TRUE}
week8_tbl %>% 
  select(gender, timeEnd, mq1q6, mq8q10) %>% 
  write.csv("../shiny_week8/week8_shiny.csv", row.names = FALSE)
```