---
title: "PSY 8712 Week 8 Project"
author: "Delaney Ross"
output:
  html_document:
    output_dir: out
---

# **Reproducible Image and Online Resources:**
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link.](add in the mybinder.org link once project is finalized, make sure to add runtime.txt and install.R files)
An interactive web app is available by [clicking this link instead.](add in the shiny app from Part 3 here)

# **Script Settings and Resources**
```{r script_settings, echo = TRUE, message = FALSE, warning = FALSE, results = 'hide'}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
#load necessary libraries here
library(tidyverse)
```

# **Data Import and Cleaning**
This section imports and cleans the data file, converts times to POSIX format, converts condition and gender to factor, and reverse codes q5. I used mutate to make these conversions as it seemed the most efficient method and I subtracted q5 from the sum of the maximum and minimum of this question as it was the most straightforward way to reverse code the column.
```{r data_import, echo = TRUE}
week8_tbl <- read.csv("../data/week3.csv") %>% 
  mutate(
    timeStart = ymd_hms(timeStart),
    timeEnd = ymd_hms(timeEnd),
    condition = factor(condition,
                       levels = c("A", "B", "C"),
                       labels = c("Block A", "Block B", "Block C")),
    gender = factor(gender,
                    levels = c("M", "F"),
                    labels = c("Male", "Female")),
    q5 = (1 + 5) - q5
  )
```

# **Visualization**
This section displays the data from q1 through q6 as well as a scatterplot of the mean scores of q1 through q6 and the mean scores of q8 through q10. *Add why I did it this way once this section is done*

# **Analysis**

# **Data Export**